---
title: "ESM204_HW2"
author: "Mia Guarnieri"
date: "4/20/2022"
output: html_document
---

1. For each irrigation district, plot the marginal abatement cost data (from the data provided) and estimate a linear regression model with zero intercept. These estimated linear regressions will be your estimates of the marginal abatement cost curve (one for each irrigation district), which you will use for the remainder of this analysis. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(patchwork)

wd <- read_csv(here("data", "Water_Districts.csv"))

kern <- wd %>% 
  select(Reduction, MC_Kern)

mojave <- wd %>% 
  select(Reduction, MC_Mojave)

antelope <- wd %>% 
  select(Reduction, MC_Antelope)

ventura <- wd %>% 
  select(Reduction, MC_Ventura)

#Kern graph
kp <- ggplot(kern, aes(x = Reduction, y = MC_Kern)) +
  geom_line() +
  labs(x = "Acre Feet Reduction",
       y = "$/Acre Foot",
       title = "Kern")

#Mojave graph
mp <- ggplot(mojave, aes(x = Reduction, y = MC_Mojave)) +
  geom_line()+
  labs(x = "Acre Feet Reduction",
       y = "$/Acre Foot",
       title = "Mojave")

#Antelope graph
ap <- ggplot(antelope, aes(x = Reduction, y = MC_Antelope)) +
  geom_line()+
  labs(x = "Acre Feet Reduction",
       y = "$/Acre Foot",
       title = "Antelope")

#Ventura graph
vp <- ggplot(ventura, aes(x = Reduction, y = MC_Ventura)) +
  geom_line()+
  labs(x = "Acre Feet Reduction",
       y = "$/Acre Foot",
       title = "Ventura")

#combine
(kp + mp)/(ap + vp)


#linear models
kern_model <- lm(data = kern, MC_Kern ~ 0 + Reduction)
kern_coeff <- kern_model$coefficient[1]

mojave_model <- lm(data = mojave, MC_Mojave ~ 0 + Reduction)
mojave_coeff <- mojave_model$coefficient[1]

antelope_model <- lm(data = antelope, MC_Antelope ~ 0 + Reduction)
antelope_coeff <- antelope_model$coefficient[1]

ventura_model <- lm(data = ventura, MC_Ventura ~ 0 + Reduction)
ventura_coeff <- ventura_model$coefficient[1]

#lm graphs
klm <- ggplot(kern, aes(x = Reduction, y = MC_Kern)) +
  geom_point(color = "lightgrey") +
  geom_smooth(method='lm', se=FALSE, color = "turquoise4") + 
  theme_minimal() + 
  labs(x = "Acre Feet Reduction",
       y = "$/Acre Foot",
       title = "Kern")

mlm <- ggplot(mojave, aes(x = Reduction, y = MC_Mojave)) +
  geom_point(color = "lightgrey") +
  geom_smooth(method='lm', se=FALSE, color = "turquoise4") + 
  theme_minimal() + 
  labs(x = "Acre Feet Reduction",
       y = "$/Acre Foot",
       title = "Mojave")

alm <- ggplot(antelope, aes(x = Reduction, y = MC_Antelope)) +
  geom_point(color = "lightgrey") +
  geom_smooth(method='lm', se=FALSE, color = "turquoise4") + 
  theme_minimal() + 
  labs(x = "Acre Feet Reduction",
       y = "$/Acre Foot",
       title = "Antelope")

vlm <- ggplot(ventura, aes(x = Reduction, y = MC_Ventura)) +
  geom_point(color = "lightgrey") +
  geom_smooth(method='lm', se=FALSE, color = "turquoise4") + 
  theme_minimal() + 
  labs(x = "Acre Feet Reduction",
       y = "$/Acre Foot",
       title = "Ventura")

#combine
(klm + mlm)/(alm + vlm)
```

2. Using your estimated marginal abatement cost curves, derive each district’s demand curve for water. In other words, how much would each district be willing to pay for the right to use the first AF of water, second AF, etc.? Plot each district’s demand curve on a single graph. Which sector is willing to pay the most for the first AF of water? 

```{r}
#predicted marginal cost based on linear model
k_base <- tibble(Reduction = 0:150)
k_pred <- predict(kern_model, newdata = k_base)
kdem <- k_base %>% 
  mutate(kpmc = k_pred,
         kd = 150 - Reduction)

m_base <- tibble(Reduction = 0:140)
m_pred <- predict(mojave_model, newdata = m_base)
mdem <- m_base %>% 
  mutate(mpmc = m_pred,
         md = 140 - Reduction)

a_base <- tibble(Reduction = 0:220)
a_pred <- predict(antelope_model, newdata = a_base)
adem <- a_base %>% 
  mutate(apmc = a_pred,
         ad = 220 - Reduction)

v_base <- tibble(Reduction = 0:245)
v_pred <- predict(ventura_model, newdata = v_base)
vdem <- v_base %>% 
  mutate(vpmc = v_pred,
         vd = 245 - Reduction)

#plot
ggplot() +
  geom_line(kdem, mapping = aes(x = kd, y = kpmc, color = "a")) +
  geom_line(mdem, mapping = aes(x = md, y = mpmc, color = "b")) +
  geom_line(adem, mapping = aes(x = ad, y = apmc, color = "c")) +
  geom_line(vdem, mapping = aes(x = vd, y = vpmc, color = "d")) +
  scale_color_manual(values = c("blue", "darkgreen", "purple", "magenta"),
                     labels = expression("Kern", "Mojave", "Antelope", "Ventura")) + 
  labs(x = "Demand (Acre Feet)",
       y = "Price",
       color = "District") +
  theme_minimal()
```

3. Here you will analyze three alternative policies for reducing water use among these irrigation districts. In total, these irrigation districts will need to reduce water consumption from the current 755 AF down to 500 AF. For each intervention listed below, perform the following calculations: 
(1) calculate the stringency of the policy (defined below for each intervention) required to achieve the 500 AF target
(2) calculate the total cost of meeting the target using that approach
(3) calculate the cost to each district
(4) calculate the tax revenue generated. 

a. Cap without trade. Reduce each district’s water use by the same fraction (e.g., 1/3 of current baseline use), so the 500 AF target is met. Trade is not allowed. Stringency is defined as the magnitude of the fraction. 
⅓ Current (i.e. baseline) water use in these districts 1 is: Kern = 49.5 AF, Mojave = 46.2 AF, Antelope = 72.6 AF, and Ventura = 80.85 AF.

```{r}
kern_price <- kern_coeff * 50.655
mojave_price <- mojave_coeff * 47.278
antelope_price <- antelope_coeff * 74.394
ventura_price <- ventura_coeff * 82.737
```


b. Tax on water use. A single tax is implemented on all water use in each of the four districts, such that water use is reduced to the 500 AF target. Stringency is defined as the magnitude of the tax. 

```{r}
km_join <- full_join(kdem, mdem, by = "Reduction")

kma_join <- full_join(km_join, adem, by = "Reduction")

demand_sum <- full_join(kma_join, vdem, by = "Reduction")

demand_sum[is.na(demand_sum)] <- 0

demand_sum <- demand_sum %>% 
  mutate(aggregate_demand = kd + md + ad + vd,
         aggregate_mc = kpmc + mpmc + apmc + vpmc) %>% 
  select(Reduction, aggregate_demand, aggregate_mc)

#plot
ggplot() +
  geom_line(kdem, mapping = aes(x = kd, y = kpmc, color = "a")) +
  geom_line(mdem, mapping = aes(x = md, y = mpmc, color = "b")) +
  geom_line(adem, mapping = aes(x = ad, y = apmc, color = "c")) +
  geom_line(vdem, mapping = aes(x = vd, y = vpmc, color = "d")) +
  geom_line(demand_sum, mapping = aes(x = aggregate_demand, y = aggregate_mc, color = "e")) +
  scale_color_manual(values = c("blue", "darkgreen", "purple", "magenta", "darkorange1"),
                     labels = expression("Kern", "Mojave", "Antelope", "Ventura", "Aggregate")) + 
  labs(x = "Demand (Acre Feet)",
       y = "Price",
       color = "District") +
  theme_minimal()


#second attempt
agg_coeff <- (1/kern_coeff) + (1/mojave_coeff) + (1/antelope_coeff) + (1/ventura_coeff)

agg_red_price <- (755-500) * agg_coeff

#prices
kern_price3b <- kern_coeff * 80.72
mojave_price3b <- mojave_coeff * 98.363
antelope_price3b <- antelope_coeff * 164.573
ventura_price3b <- ventura_coeff * 89.181
```


4. a)

```{r}
kern_price4a <- kern_coeff * 59.61
mojave_price4a <- mojave_coeff * 55.636
antelope_price4a <- antelope_coeff * 87.428
ventura_price4a <- ventura_coeff * 97.363
```


